\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=black}
\usepackage{setspace}

\onehalfspacing
\pagestyle{empty}
\setlength{\parindent}{0pt}

\titleformat{\section}{\normalsize\bfseries\centering}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

\setlist[itemize]{nosep, leftmargin=1.5em, label=\textbullet}

\begin{document}

\begin{center}
    {\LARGE \textbf{Logan George}} \\[4pt]
    \href{mailto:logangeorge01@gmail.com}{logangeorge01@gmail.com} \textbar\ 913.747.5478 \textbar\ \href{https://lagsoftware.com}{lagsoftware.com} \\
    \href{https://github.com/logangeorge01}{github.com/logangeorge01} \textbar\ \href{https://linkedin.com/in/logangeorge}{linkedin.com/in/logangeorge}
\end{center}

\section{Education}

\textbf{University of Alabama (2019--2023)}
\begin{itemize}
    \item B.S.: Computer Science, Minor: Mathematics
\end{itemize}

\textbf{Achievements}
\begin{itemize}
    \item ACT: 34, SAT: 1540, National Merit Finalist
\end{itemize}

\section{Employment}

\textbf{Microsoft (June 2023-Present)}
\begin{itemize}
    \item Software Engineer
    \item Working on the Kubernetes platform of an air-gapped Azure control plane. Owning a service mapping customer clusters as deployable locations in Azure. Also owning a service acting as a Kubernetes control plane for custom resources running on Windows.
\end{itemize}

\textbf{Microsoft (May-August 2022)}
\begin{itemize}
    \item Software Engineering Intern
    \item Enabling Azure container registries to be run on edge environments. E.g.\ syncing Docker images between Azure cloud, on premises datacenters, and IoT devices.
\end{itemize}

\textbf{WellSky (May-August 2021)}
\begin{itemize}
    \item Software Engineering Intern
    \item Wrote features and fixed bugs for the company's Blood Transfusion web application in .NET and Angular.
\end{itemize}

\textbf{Integrity Inspired Solutions (May--August 2019)}
\begin{itemize}
    \item Software Engineering Intern
    \item Built a social media app for iOS and Android with Nativescript (Angular) and Firebase.
\end{itemize}

\textbf{Atonix Digital (May--August 2018)}
\begin{itemize}
    \item Software Engineering Intern
    \item Created a data analysis page in .NET on the Asset360 platform for an IoT network of sensors, implementing various AWS technologies.
\end{itemize}

\section{Projects}

\begin{itemize}
    \item PredictChain -- Event prediction market built on the Solana blockchain. Rust smart contracts. Automated market maker prices tokens in liquidity pool.
    \item Fibre -- A social, personalized clothes shopping feed. iOS app (Swift), Node.js/Express backend on Heroku, PostgreSQL database. Beta app supported 100s of users and was pitched to VCs.
\end{itemize}

\section{Skills}

\textbf{Languages:}
\begin{itemize}
    \item C\#, Go, Python, JavaScript
\end{itemize}

\textbf{Miscellaneous:}
\begin{itemize}
    \item Kubernetes, Docker, Git
\end{itemize}

\end{document}